TacticToe: Learning to Prove with Tactics

### 2018-02-19 tactictoe_jv.tex
More

\section{Proof Recording}\label{sec:recording}
Recording proofs in an LCF-style proof assistant can be done at different
levels.
In \holfour all existing approaches relied on modifying the kernel. This was
used
either to export the primitive inference
steps~\cite{Wong95recordingand,DBLP:conf/itp/KumarH12}
or to record dependencies of theorems~\cite{tgck-cpp15}. This was not suitable
for our
purpose of learning proving strategies at the intermediate tactic level. We
therefore
discuss recording proofs in an LCF-style proof assistant, with the focus on
\holfour
in this section.
<
Rather than relying on the underlying programming language, we parse the
original theory file containing proof scripts. This enables us to extract the
code of each tactic.
Working with the string representation of a tactic is better that working with
its value:
\begin{itemize}
\item Equality between two functions is easy to compute from
their string representation and therefore we can avoid
predicting the same tactic over and over again.
\item
The
results of
\tactictoe can be returned in a readable form to the user. In this way, the
user can learn from the feedback, analyze the proof and possibly improve on it.
An other point is that \tactictoe does not need to be installed to run
proof scripts generated by \tactictoe. In this way, the further development of
\tactictoe are not affecting the robustness of \holfour.
\item
It is difficult (probably impossible) to transfer \sml values
between theories as they are not run in the same \holfour session. In contrast,
\sml code can be exported, imported.
\item To produce a tactic value form a code is easy in \sml, which can be
achieved by using a reference to a tactic and update it with the function
\texttt{use}.
\end{itemize}

>>>>

\section{Proof Recording}\label{sec:recording}
Recording proofs in an LCF-style proof assistant can be done at different
levels.
In \holfour all existing approaches relied on modifying the kernel. This was
used
either to export the primitive inference
steps~\cite{Wong95recordingand,DBLP:conf/itp/KumarH12}
or to record dependencies of theorems~\cite{tgck-cpp15}. This was not suitable
for our
purpose of learning proving strategies at the intermediate tactic level. We
therefore
discuss recording proofs in an LCF-style proof assistant, with the focus on
\holfour
in this section.
%
Rather than relying on the underlying programming language, we parse the
original theory file containing proof scripts. This enables us to extract the
code of each tactic.
Working with the string representation of a tactic is better than working with
its value:
\begin{itemize}
\item Equality between two functions is easy to compute from
their string representation, which allows us to avoid
predicting the same tactic repeatedly.
\item
The
results of
\tactictoe can be returned in a readable form to the user. In this way, the
user can learn from the feedback, analyze the proof and possibly improve on it.
Furthermore \tactictoe does not need to be installed to run
proof scripts generated by \tactictoe. In this way, the further development of
\tactictoe does not affect the robustness of \holfour.
\item
It is difficult (probably impossible) to transfer \sml values
between theories, since they are not run in the same \holfour session. In contrast,
\sml code can be exported and imported.
\item To produce a tactic value form a code is easy in \sml, which can be
achieved by using a reference to a tactic and update it with the function
\texttt{use}.
\end{itemize}
